Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-10-08 talk/index.Rmd
first draft experimental design diagram

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(tidyverse)
library(xaringanthemer)
library(xaringanExtra)
library(icons)

@@

>>>>

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(tidyverse)
library(xaringanthemer)
library(xaringanExtra)
library(icons)
library(widgetframe)
library(DiagrammeR)

@@

---
class: center

# Experimental Design

```{r, fig.align='right', fig.retina=3, echo = FALSE}
my_design <- DiagrammeR::mermaid("
graph TD

classDef classOne fill:#c8e2fa,stroke:#333,stroke-width:4px
classDef classTwo fill:#e8e9eb,stroke:#333,stroke-width:4px

A[<center>Introduction to research question <br> Do religious people report higher well-being?</center>] 
A ==>B[<center>Report prior beliefs <br> How likely do you think it is that people who are more religious generally report higher well-being?</center>]
B ==>C[<center>Single-analyst condition</center>]
B ==>D[<center>Multi-consistent condition</center>]
B ==>E[<center>Multi-inconsistent condition</center>]
F[<center>Report dependent variables <br> Posterior beliefs, credibility of the results, confidence in the effect size estimate, bias, error, and discretion</center>]
C ==>F
D ==>F
E ==>F

class A classOne
class B classTwo
class C classOne
class D classTwo
class E classOne
class F classTwo

                           ")
widgetframe::frameWidget(my_design)
```
